Computational methods in landscape ecology

### 2024-05-17 Manuscript.qmd
Add new MS and Sections structure

<!-- FIXME: Add Authors -->
<!-- FIXME: Add sections -->

{{< include Sections/introduction.qmd >}}
{{< include Sections/spatial-planning.qmd >}}

>>>>

<!-- FIXME: Update Authors -->
<!-- FIXME: Add sections -->

{{< include Sections/introduction.qmd >}}
{{< include Sections/spatial-pattern.qmd >}}
{{< include Sections/spatial-planning.qmd >}}
